EinsteinPy: Python for General Relativity\footnote{Released on July, 15th, 2019}

### 2020-01-04 paper.tex
edits take-II

%# calculates the trajectory
%ans = obj.calculate_trajectory(
    %end_lambda=end_lambda, OdeMethodKwargs={"stepsize": stepsize}, return_cartesian=True
%)
%\end{minted}
\subsection{plotting}
\subsection{symbolic}
General Relativity required heavy mathematical formulation to derive and describe various tensors attributing to various features essential for cogent description of a arbitrary space-time. We would describe the various quantities currently supported by this module while maintaining brevity. 
\subsection{hypersurface}
This module provides with basic computational functions which are essential for modelling the space-like hypersurface for any spacetime geometry. Currently module has implementation for Schwarzschild geometry with conversion functions from Schwarzschild coordinates to 3-D spherical coordinates and some plotting utilities. The whole module is expected to extend for providing a superclass for implementations related to gravitationl lensing simulations and numerical calculations of null geodesics on hypersurfaces and deviation angles for systems which are relevant to relativistic astrophysical problems. A small code snippet for plotting the hypersurface is as follows:
%\begin{minted}[linenos]{python}
%# importing the modules
from einsteinpy.hypersurface import SchwarzschildEmbedding
from astropy import units as u

>>>>

%# calculates the trajectory
%ans = obj.calculate_trajectory(
    %end_lambda=end_lambda, OdeMethodKwargs={"stepsize": stepsize}, return_cartesian=True
%)
%\end{minted}
\subsection{plotting}
\subsection{symbolic}
General Relativity required heavy mathematical formulation to derive and describe various tensors attributing to various features essential for cogent description of a arbitrary space-time. We would describe the various quantities currently supported by this module while maintaining brevity. Each quantity has its own class, even scalars, which are treated as 0\textsuperscript{th} order tensors.

\subsubsection{BaseRelativityTensor}
This is a base class from which other tensors are derived. The user can use this class to create his/her own tensor while using the various in-built functions provided by this class. The class also maintains the indicial configuration of the tensor(contravariant and co-variant indices), calculates the free variables used in describing the tensor other than those which depicts the axis of space-time itself (e.g. t,x,y,z). The class has a function to convert the symbolic tensorial quantities into functions where actual numerical values can be substitued.

This class along with its parent class contains the following functions/properties.
\begin{itemize}
\item \texttt{order} (Property) : Returns the order of the tensor. 
\item \texttt{config} (Property) : Returns the arrangement of contravariant(upper)/covariant(lower) indices of the tensor. For example, 'ulll'.
\item \texttt{parent\_metric} (Property) : Returns the metric tensor of the space-time associated with the tensor, if present. Else returns \texttt{None}.
\item \texttt{tensor} (Function) : Returns the tensorial quantity contained within the class instance.
\item \texttt{subs} (Function) : Returns a new tensor upon substitution of current variables with new variables/values.
\item \texttt{simplify} (Function) : Returns a tensor contain simplified expressions from the current tensor.
\item \texttt{symbols} (Function) : Returns the symbols denoting each axis of the space-time.
\item \texttt{tensor\_lambdify} (Function) : Returns lambdified function of symbolic tensors. This means that the returned functions can accept numerical values and return numerical quantities.
\end{itemize}

\subsubsection{MetricTensor}
Metric Tensor describes the differential length elements required to measure distance in a curved(also applies to flat) space-time. It is a second order tensor and is fundamental to describe any space-time geometry. The \texttt{MetricTensor} class, being inherited from \texttt{BaseRelativityTensor}, inherits all its functions and also have some functions and constraints of its own. For example, metric tensor is bound to be a second order tensor.

The defined class functions are :
\begin{itemize}
\item \texttt{change\_config} : returns a different instance of the same class with different index (contravariant or covariant) configuration. 
\item \texttt{inv} : returns inverse of the metric
\end{itemize}

\subsubsection{ChristoffelSymbols}
Although Christoffel Symbols are belong to class of pseudo-tensors, it is inherited from \texttt{BaseRelativityTensor} to maintain homogenity within the module. Bein inherited from \texttt{BaseRelativityTensor}, it already supports the functions of its parent class and imposes some restrictions of its own, such as order of the tensor should be 3.

Instance of the class can be made by directly passing a 3\textsuperscript{rd} order tensor or can be obtained using the following classmethods
\begin{itemize}
\item \texttt{from\_metric} : Calculates christoffel symbols from a given instance of \texttt{MetricTensor} class.
\end{itemize}

The defined class function(s) are : 
\begin{itemize}
\item \texttt{change\_config} : returns a different instance of the same class with different index (contravariant or covariant) configuration. 
\end{itemize}

\subsubsection{RiemannCurvatureTensor}
This quantity is the most extensive measure of curvature of a sapce-time. It is inherited from \texttt{BaseRelativityTensor} and supports all the functions of its parent class.

Instance of the class can be made by directly passing a 4\textsuperscript{th} order tensor or can be obtained using the following classmethods
\begin{itemize}
\item \texttt{from\_metric} : Calculates Riemann Tensor from a given instance of \texttt{MetricTensor} class.
\item \texttt{from\_christoffels} : Calculates Riemann Tensor from a given instance of \texttt{ChristoffelSymbols} class.
\end{itemize}

The defined class function(s) are : 
\begin{itemize}
\item \texttt{change\_config} : returns a different instance of the same class with different index (contravariant or covariant) configuration. 
\end{itemize}

\subsubsection{RicciTensor}
This tensor is used in solving Eintein's  equation and basically contraction of Riemann Curvature Tensor.  It is inherited from \texttt{BaseRelativityTensor} and supports all the functions of its parent class.

Instance of the class can be made by directly passing a 2\textsuperscript{nd} order tensor or can be obtained using the following classmethods
\begin{itemize}
\item \texttt{from\_metric} : Calculates Ricci Tensor from a given instance of \texttt{MetricTensor} class.
\item \texttt{from\_christoffels} : Calculates Ricci Tensor from a given instance of \texttt{ChristoffelSymbols} class.
\item \texttt{from\_riemann} : Calculates Ricci Tensor from a given instance of \texttt{RiemannCurvatureTensor} class.
\end{itemize}

The defined class function(s) are : 
\begin{itemize}
\item \texttt{change\_config} : returns a different instance of the same class with different index (contravariant or covariant) configuration. 
\end{itemize}

\subsubsection{RicciScalar}
It is a scalar quantity obtained by contracting a given Ricci Tensor. It is inherited from \texttt{BaseRelativityTensor} and supports all the functions of its parent class. Being a scalar quantity, it does not support \texttt{change\_config} unlike other tensors as discussed above.

Instance of the class can be made by directly passing a symbolic expression or can be obtained using the following classmethods
\begin{itemize}
\item \texttt{from\_metric} : Calculates Ricci Scalar from a given instance of \texttt{MetricTensor} class.
\item \texttt{from\_christoffels} : Calculates Ricci Scalar from a given instance of \texttt{ChristoffelSymbols} class.
\item \texttt{from\_riemann} : Calculates Ricci Scalar from a given instance of \texttt{RiemannCurvatureTensor} class.
\item \texttt{from\_riccitensor} : Calculates Ricci Scalar from a given instance of \texttt{RicciTensor} class.
\end{itemize}

The defined class properties are : 
\begin{itemize}
\item \texttt{expr} : returns the scalar symbolic expression contained in the class. 
\end{itemize}

\subsubsection{Other Defined Quantities}
As the library is in heavy development, new quantities are being added as and when required. Some other quantities currently supported are listed below. The quantities are all inherited from \texttt{BaseRelativityTensor}, and a similar API (same as that of discussed above) has been implemented to maintain compatiblity and homegenity. The class names denote usual quantities relevant to General Relativity.

\begin{itemize}
\item \texttt{EinsteinTensor}
\item \texttt{StressEnergyMomentumTensor}
\item \texttt{WeylTensor}
\item \texttt{SchoutenTensor}
\end{itemize}

Further, various constants like $c$(speed of light), $G$(Gravitational constant) are defined in their symbolic forms, for use within the symbolic module.

\subsection{hypersurface}
This module provides with basic computational functions which are essential for modelling the space-like hypersurface for any spacetime geometry. Currently module has implementation for Schwarzschild geometry with conversion functions from Schwarzschild coordinates to 3-D spherical coordinates and some plotting utilities. The whole module is expected to extend for providing a superclass for implementations related to gravitationl lensing simulations and numerical calculations of null geodesics on hypersurfaces and deviation angles for systems which are relevant to relativistic astrophysical problems. A small code snippet for plotting the hypersurface is as follows:
%\begin{minted}[linenos]{python}
%# importing the modules
from einsteinpy.hypersurface import SchwarzschildEmbedding
from astropy import units as u
